---
title: "R Notebook"
output: html_notebook
---

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

LIBRARIES
```{r}
if (!require(tidyverse)) install.packages("tidyverse")
if (!require(skimr)) install.packages("skimr")
if (!require(DataExplorer)) install.packages("DataExplorer")
if (!require(dplyr)) install.packages("dplyr")
if (!require(lubridate)) install.packages("lubridate")
if (!require(readr)) install.packages("readr")
if (!require(VIM)) install.packages("VIM")
if (!require(colorspace)) install.packages("colorspace")
if (!require(grid)) install.packages("grid")
if (!require(zoo)) install.packages("zoo")

# Laden der Libraries
library(tidyverse)
library(skimr)
library(DataExplorer)
library(dplyr)
library(lubridate)
library(readr)
library(VIM)
library(colorspace)
library(grid)
library(zoo)
```

Einlesen der Daten
```{r}
kiwo <- read.csv("kiwo.csv")
wetter <- read.csv("wetter.csv")
umsatz_train <- read.csv("train.csv")
umsatz_test <- read.csv("test.csv")
feiertage <- read.csv("Feiertage.csv", sep = ";")
schulferien <- read.csv("Schulferien.csv")
```

Sicherstellen, dass Datum in allen Datensätzen gleiches Format
```{r}
umsatz_train$Datum <- ymd(umsatz_train$Datum)
umsatz_test$Datum <- ymd(umsatz_test$Datum)
wetter$Datum <- ymd(wetter$Datum)
kiwo$Datum <- ymd(kiwo$Datum)
schulferien$Datum <- ymd(schulferien$Datum)
feiertage$Datum <- as.Date(feiertage$Datum, format = "%d.%m.%Y")
```

Hinzufügen der Spalte "wochentage"
```{r}
umsatz_train$wochentag <- weekdays(umsatz_train$Datum)
umsatz_test$wochentag <- weekdays(umsatz_test$Datum)
```

Hinzufügen der Spalte "jahreszeit"
```{r}
yq <- as.yearqtr(as.yearmon(umsatz_train$Datum, "%m/%d/%Y") + 1/12)
# Berechnung der Jahreszeit
umsatz_train$jahreszeit <- factor(format(yq, "%q"), levels = 1:4, 
      labels = c("Winter", "Frueling", "Sommer", "Herbst"))
yq <- as.yearqtr(as.yearmon(umsatz_test$Datum, "%m/%d/%Y") + 1/12)
# Berechnung der Jahreszeit
umsatz_test$jahreszeit <- factor(format(yq, "%q"), levels = 1:4, 
      labels = c("Winter", "Frueling", "Sommer", "Herbst"))
rm(yq)
```

Hinzufügen der Spalte "monat"
```{r}
umsatz_train <- mutate(umsatz_train, monat = factor(format(Datum, "%m")))
umsatz_test <- mutate(umsatz_test, monat = factor(format(Datum, "%m")))
```

Zusammenfügen der Datensätze und umwandeln der Variablen "Kielerwoche", "Feiertag" und "Ferien" in Boolean
```{r}
merged_data_train <- umsatz_train %>%
  left_join(wetter, by = "Datum") %>%
  left_join(kiwo, by = "Datum") %>%
  left_join(feiertage, by = "Datum") %>%
  left_join(schulferien, by = "Datum")
# Umwandeln in Boolean
merged_data_train$KielerWoche <- !is.na(merged_data_train$KielerWoche)
merged_data_train$Feiertag <- !is.na(merged_data_train$Feiertag)
merged_data_train$Ferien <- !is.na(merged_data_train$Ferien)
merged_data_train <- as_tibble(merged_data_train)
#Abspeichern
write.csv(merged_data_train, file="joinedData_train.csv")
```

```{r}
merged_data_test <- umsatz_test %>%
  left_join(wetter, by = "Datum") %>%
  left_join(kiwo, by = "Datum") %>%
  left_join(feiertage, by = "Datum") %>%
  left_join(schulferien, by = "Datum")
# Umwandeln in Boolean
merged_data_test$KielerWoche <- !is.na(merged_data_test$KielerWoche)
merged_data_test$Feiertag <- !is.na(merged_data_test$Feiertag)
merged_data_test$Ferien <- !is.na(merged_data_test$Ferien)
merged_data_test <- as_tibble(merged_data_test)
#Abspeichern
write.csv(merged_data_test, file="joinedData_test.csv")
```

```{r}
rm(feiertage)
rm(wetter)
rm(kiwo)
rm(schulferien)
rm(umsatz_train)
rm(umsatz_test)
```

#train_data$Wettercode <- na.locf(train_data$Wettercode, fromLast = TRUE, na.rm = FALSE)

```{r}
train_data <- read.csv("joinedData_train.csv")
plot <- aggr(train_data, combined=TRUE, numbers=TRUE)
print(plot)
```

```{r}
train_data <- hotdeck(train_data, imp_var = FALSE)
```

```{r}
test_data <- read.csv("joinedData_test.csv")
plot <- aggr(test_data, combined=TRUE, numbers=TRUE)
print(plot)
```

```{r}
test_data <- hotdeck(test_data, imp_var = FALSE)

```

Umwandeln der numerischen Variablen "Temperatur", "Windgeschwindigkeit" und "Wettercode" in Kategorien
```{r}
train_data$Windgeschwindigkeit_labels <- cut(train_data$Windgeschwindigkeit, breaks = c(0,10.7,20.7,37), labels=c("Brise", "Wind","Sturm"), right=FALSE)
test_data$Windgeschwindigkeit_labels <- cut(test_data$Windgeschwindigkeit, breaks = c(0,10.7,20.7,37), labels=c("Brise", "Wind","Sturm"), right=FALSE)

train_data$Temperatur <- as.numeric(as.character(train_data$Temperatur))
train_data$Temperatur_labels <- cut(train_data$Temperatur, breaks = c(-20,1,11,21,31,45), labels=c("eisig", "kalt", "moderat", "sommerlich", "heiß"), right=FALSE)

test_data$Temperatur <- as.numeric(as.character(test_data$Temperatur))
test_data$Temperatur_labels <- cut(test_data$Temperatur, breaks = c(-20,1,11,21,31,45), labels=c("eisig", "kalt", "moderat", "sommerlich", "heiß"), right=FALSE)

train_data$Wettercode <- as.numeric(as.character(train_data$Wettercode))
train_data$Wettercode_labels <- cut(train_data$Wettercode, breaks = c(0,14,99), labels=c("Trocken","RegenGewitter"), right=FALSE)

test_data$Wettercode <- as.numeric(as.character(test_data$Wettercode))
test_data$Wettercode_labels <- cut(test_data$Wettercode, breaks = c(0,14,99), labels=c("Trocken","RegenGewitter"), right=FALSE)
```


```{r}
write.csv(train_data, file="preparedTrainData.csv")
write.csv(test_data, file="preparedTestData.csv")
```

```{r}
grp_warengruppe = test_data %>% arrange(Datum)
```


